\section{\GSAC: Merging Group Signatures and Anonymous
  Credentials}
\label{sec:gsac}

Before moving into our full-fledged scheme for universal anonymous signatures,
we take a first step which, albeit somehow obvious and simple, helps understand
our final goal. Namely, we give a scheme that combines in a quite direct manner
the functionality of group signature schemes, and that of anonymous credential
schemes.

\paragraph{Why is this merge necessary in the real world?} %
Despite being an \emph{a priori} simple combination of both schemes we argue
that such a combination:

\begin{itemize}
\item Enables a natural way to incorporate accountability within 
  privacy-preserving identities. Furthermore, it does so in a formal way,
  via the traceability notion and, crucially, the non-frameability one
  (which is not present in anonymous credentials).
\item Provides meaning to the conventional \Open functionality of group
  signatures, which traditionally has only required that an abstract concept of
  ``identity'' be returned. Concretely, assuming honest issuance (which is
  already a requirement in anonymous credentials; and in group signatures for
  traceability), we can make specific claims about the attributes associated to
  de-anonymized signers. Otherwise, without integrating attributes within the
  issued credentials, the value returned by \Open serves barely for blacklisting
  or similar functionalities -- but otherwise gives no information straight away
  about the signer's identity, forcing implementors to rely to non-cryptographic
  means to retrieve such information.
\end{itemize}

\paragraph{Intuition for our design and construction.} %
Functionally, we combine both worlds. Namely, a user can get as many credentials
as s/he wants -- although all are bound to the same user key --, and signatures
(or credential presentations) of the same credential must be unlinkable. In this
simplified first step, we restrict to selective attribute disclosure, meaning
that signatures produced by a credential reveal only a subset of the attributes
in that credential. Given such a signature, there is a trusted opener who can
de-anonymize its signer, producing back its public key, as well as a proof of
correct opening.

With respect to the model, privacy-wise this direct combination requires that
any two signatures (credential presentations) reveal nothing about the
credential used to produce them, beyond the revealed attributes.
Security-wise we stick to the conventional separation of
unforgeability-related properties in group signatures. That is, traceability
requires that, in the presence of an honest issuer, all valid signatures must
originate from a credential issued by the issuer; and, from the AC domain, we
import the requirement that no user can claim having attributes that have not
been issued to a single credential. As in group signatures, if the issuer is
corrupt, all we can hope for is that honest users do not get undeserved blame;
but, other than that, the adversary can obviously obtain credentials with
arbitrary attributes. Still, note that this is a clear gain with respect to
conventional anonymous credential systems, which offer no security against a
malicious issuer.
%
Finally, in this first step, we restrict ourselves to signatures/presentations
involving only one credential, to a system with only one issuer and opener  and,
as stated, to selective attribute disclosure.

\input{model-gsac.tex}
\input{construction-gsac.tex}
\input{security-gsac.tex}
\input{extensions-gsac.tex}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:
